### 2023-01-25 Draft_GFC.tex
backup

\tikzset{
  mycross/.pic={
    \draw[pic actions] 
      (-2pt,0) -- (2pt,0)
      (0,-2pt) -- (0,2pt);
  },
}
 \newcolumntype{C}[1]{>{\centering\arraybackslash$}p{#1}<{$}}
\begin{document}
\section{Introduction}

The main objective of our study is to be able to decide whether the texture of a grey-level image is isotropic or not. By the texture of an image, we mean the microscopic structure that is captured by the covariance function at the pixels scale. In order to achieve this goal, we propose a methodology built on a statistical test for which all steps are rigorously validated. The originality of our approach is to stick on the geometrical features of the image without trying to identify the full distribution of the underlying random field that is supposed to serve as a model. More precisely, our observable statistic will be the black domain perimeter in thresholded images.

@@

Implementations of this type of method can be found in medical imaging and image analysis in general, cosmology, hydrology, sea waves modeling, etc. As an example, let us exhibit some medical images that can be handled with our methodology. In this introductory part, we just show the images and a first tentative of descriptive statistics. The statistical results that we are able to infer from our methodology is detailed at the end of the present paper (see Section 4.3). 
%\paragraph{Study of the anisotropic nature of bone X-rays.}
%\textcolor{blue}{\textbf{Dans le papier, ils disent qu'ils ont 174 images, j'en ai 245 dans le dossier.}}
%The X-ray images are from an retrospective multi-centric study that was conducted at
%three French research hospitals (Amiens, Orleans and Cochin in Paris). ({\sc details necessaires?})
%Patients were recruited from a program originated by the hospital of
%Orleans between Nov. 2004 and Feb. 2006. 
We analyzed $245$ X-ray images of calcaneus bones in order to detect the eventual anisotropic nature of the microarchitecture.
%to assess if the distribution of the images is isotropic or not.  and used a geometric tool to do so, but first and for most, their is a necessary post processing step which is to  to stationarize the images, in order to be in the correct framework.
We first applied a preprocessing step in order to get stationary images 
%This step is performed by sustracting the trend which is represented by a plane obtained via a mean-square linear regression.
and then 
%Let $\alpha \in (0,1)$ and $t_{\alpha} = F^{-1}_{X}(\alpha)$ be the associated quantile of the image $X$. We 
consider the thresholded images at various quantile levels $t_{\alpha}$, \emph{i.e.} the binary images $\{X > t_{\alpha}\}$.
\begin{figure}[H]
\centering
{\includegraphics[scale=0.5]{imagesstationarisee.pdf}}
 \caption{Stationnarized image of a bone x-ray, with its associated excursion sets thresholded at the first, second and third quartile.}
\label{fig22}
\end{figure}
As observable statitics, we use 
%compute the horizontal and vertical perimeter of each thresholded image, thus obtaining for each level $t_{\alpha}$, $(P^{(1)}_{i}(t_{\alpha}))_{i \leq 245}$, count
the respective numbers of horizontal and vertical edges that separate a black pixel from a white pixel of the binary image. We name these counters as oriented perimeters, horizontal and vertical respectively. In case of an isotropic texture, the ratio of the two oriented perimeters should be close to one. At the opposite, if the observed ratio is far from one, then some anisotropy is expected in the microscopic texture of the image.

@@

The next step of our method consists in building the promised statistical test. More precisely, $\rho$ being the covariance function of the Gaussian field and $(e_1,e_2)$ being the canonical basis of $\mathbb R^2$, we consider the null hypothesis $H0:~\rho(e_1)=\rho(e_2)$ that we call "local isotropy" through a misuse of language. We exhibit a statistic depending on the ratio of the oriented perimeters that goes to one under $H0$ thanks to the CLT previoulsy established. Moreover, we prove the consistency of the proposed test. Let us insist on the fact that our test is a non-parametric one so that the alternative hypothesis reduces to $H1:~\rho(e_1)\ne \rho(e_2)$.

@@

This result extends the one given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. Using the former expression, we are also able to obtain an analytic expression for the first moment.

@@

@@

@@

with $N \sim \mathcal{N}\left(0,1\right)$. We introduce an intermediate function $p_{t}(x) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ making use of the symmetry properties of the cumulative distribution function $\Phi$, \linebreak we have $h_{t}(x) =p_{t}(x) - 1 + p_{-t}(x)$, thus the derivative of $h_{t}$ is equal to $h_{t}'(x) = p_{t}'(x) + p_{-t}'(x)$ and 

@@

\end{align*}Thus, $h_{t}'(x) = 2 \times \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}} = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}}$.

@@

\item In the case of a fully dependent field, \textit{i.e}  $\rho(e_i) = 1$, note that $\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) \right) = 0$.
\item In the case where $\rho(e_i) \sim 1$, then $\mathbb{E}\left(f^{(i)}(t) \right) \sim \frac{\sqrt{1-\rho(e_i)}}{\pi\sqrt{2}} \exp(-t^2/2)$, as in \cite{HermineAgnes}, in that case the ratio $\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)$ is invariant in regard to $t$

@@

Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$ such that $|\rho(e_i)| < 1$.

@@

Let us first start with the two cells case, which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$. Applying the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}, we get the next result. \\

@@

@@

@@

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{Variance_40_30_10_1.pdf}}
    \hspace{0.2cm}
 \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40, 30, 10,1$. }
\label{figVariance}
\end{figure}
\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{subwindowVarestimation.pdf}}
    \hspace{0.2cm}
 \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute, the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the subwindow estimation of the variance, the computations were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$, for the values $b = 1$ and $C = 40$. }
\label{figSubwindowVariance}
\end{figure}

@@

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiopvaluesubwindow.pdf}}
    \hspace{0.2cm} 
 \caption{We represent the $p_{\text{value}} = 2\mathbb{P}\left(Z \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $Z \sim \mathcal{N}(0,1)$ the computations for the variance were done using an image of size $= 4800$, $C = 40$ and the size of $T_{i}$ for the variance estimation was $240\times240$  for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
% \label{fig2}

\end{figure}
\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiopvaluetheta.pdf}}
    \hspace{0.2cm} 
 \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/12, \pi/8, \pi/6, \pi/3$ and $C = 40$.}
% \label{fig2}
\end{figure}

\paragraph{Blind angle}It is important to note that we only test a form of local isotropy, with preferential axis $(e_1,e_2)$ there exist anisotropic models where $\rho(e_1) = \rho(e_2)$, like it is the case when $\theta = \pi/4$, in that case the model is clearly anisotropic as we can see Figure and the test will accept the hypothesis. \textcolor{red}{Add discussion about this, l'erreur de type 1 et 2.}
\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiopvaluepi4.pdf}}
    \hspace{0.2cm} 
 \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/4$ and $C = 40$.}
% \label{fig2}
\end{figure}
\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
    \hspace{0.2cm} 
 \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}
% \label{fig2}
\end{figure}

@@

\subsection{Application of the local isotropy test to real world Data}

@@

three French research hospitals (Amiens, Orleans and Cochin in Paris). Patients were recruited from a program originated by the hospital of Orleans between Nov. 2004 and Feb. 2006. We analyzed $245$ X-ray images of calcaneus bones. 
We first applied a preprocessing step in order to get stationary images. This step is performed by substracting the trend which is represented by a plane obtained via a mean-square linear regression, to avoid boundarie issues, we decided to crop from a $400\times400$  image to a $300\times300$ image.

@@

 \caption{Stationnarized image of a bone x-ray, with its associated excursion sets thresholded at the first, second and third quartile.}

@@

\paragraph{Applying the local isotropy test.}The first analysis of Figure \ref{figBoxplot} suggests that an additional pre-processing step is required. We observe a cluster of points for which the ratio $\mathcal{P}_{1}(q_{\alpha})/\mathcal{P}_{2}(q_{\alpha}) < 1$, which means that the corresponding images are misoriented. Thus, before proceeding with the analysis, it is necessary to apply a $\pi/2$-rotation to these images, which amounts to interchanging the values of $\mathcal{P}_{1}(q_{\alpha})$ and $ \mathcal{P}_{2}(q_{\alpha})$, here is the new boxplot that,

@@

 \caption{For $\alpha \in [0.15, 0.99]$, we represent the boxplot of the ratio between the two oriented perimeters computed at $t_{\alpha}$ level, $\mathcal{P}^{1}(t_{\alpha}), \mathcal{P}^{2}(t_{\alpha})$, for real thresholded images of bone X-rays.}

@@

We can now proceed to apply the local isotropy test, we start by computing the ratio $R_{i}(q_{\alpha})$ for each level set of the image $U_{i}$ at quantile level $\alpha$, with then compute the $p_{value}(q_{\alpha}) = 2(1-\mathbb{P}\left(\mathcal{N} \leq \left|\overline{R}_{n}(q_{\alpha}) - 1)\right|/\overline{\sigma}_{n}(q_{\alpha})\right))$. 

@@

 \caption{For $\alpha \in [0.15, 0.99]$, we represent the $p_{value}$ of the test computed for different levels $q_{alpha}$ for real thresholded images of bone X-rays.}

@@

The $p_{value}$ is lower than $0.001$, except for extreme values of $q_{\alpha}$ (\textit{i.e} $\alpha = 0.99$), this leads us to reject $H_{0}$ of having local isotropy, furthermore, when analyzing Figure \ref{Boxplotretournee} the distribution of the ratio $\left(R_{i}(t)\right)_{i\leq n}$ seems to be invariant in regards to the threshold level as cited in \ref{casdegenerer}, this suggests that the field is highly dependent, the next step would be to estimate $\rho(e_i)$ by using the total variation of the image by applying Proposition \ref{Variationtotal}. 

@@

Looking at Figure \ref{boxplotrho}, it confirms the highly dependence behavior of the field.

>>>>

\tikzset{
  mycross/.pic={
    \draw[pic actions] 
      (-2pt,0) -- (2pt,0)
      (0,-2pt) -- (0,2pt);
  },
}
 \newcolumntype{C}[1]{>{\centering\arraybackslash$}p{#1}<{$}}
\begin{document}
\section{Introduction}
The main objective of our study is to be able to decide whether the texture of a grey-level image is isotropic or not. By the texture of an image, we mean the microscopic structure that is captured by the covariance function at the pixels scale. In order to achieve this goal, we propose a methodology built on a statistical test for which all steps are rigorously validated. The originality of our approach is to stick on the geometrical features of the image without trying to identify the full distribution of the underlying random field that is supposed to serve as a model. More precisely, our observable statistic will be the black domain perimeter in thresholded images.

@@

Implementations of this type of method can be found in medical imaging and image analysis in general, cosmology, hydrology, sea waves modeling, etc. As an example, let us exhibit some medical images that can be handled with our methodology. In this introductory part, we just show the images and a first tentative of descriptive statistics. The statistical results that we are able to infer from our methodology is detailed at the end of the present paper (see Section 4.3). 
%\paragraph{Study of the anisotropic nature of bone X-rays.}
%\textcolor{blue}{\textbf{Dans le papier, ils disent qu'ils ont 174 images, j'en ai 245 dans le dossier.}}
%The X-ray images are from an retrospective multi-centric study that was conducted at
%three French research hospitals (Amiens, Orleans and Cochin in Paris). ({\sc details necessaires?})
%Patients were recruited from a program originated by the hospital of
%Orleans between Nov. 2004 and Feb. 2006. 
We analyzed $245$ X-ray images of calcaneus bones in order to detect the eventual anisotropic nature of the microarchitecture.
%to assess if the distribution of the images is isotropic or not.  and used a geometric tool to do so, but first and for most, their is a necessary post processing step which is to  to stationarize the images, in order to be in the correct framework.
We first applied a preprocessing step in order to get stationary images 
%This step is performed by sustracting the trend which is represented by a plane obtained via a mean-square linear regression.
and then 
%Let $\alpha \in (0,1)$ and $t_{\alpha} = F^{-1}_{X}(\alpha)$ be the associated quantile of the image $X$. We 
consider the thresholded images at various quantile levels $t_{\alpha}$, \emph{i.e.} the binary images $\{X > t_{\alpha}\}$.
\begin{figure}[H]
\centering
{\includegraphics[scale=0.5]{imagesstationarisee.pdf}}
 \caption{Stationnarized bone X-ray image, with its associated excursion sets thresholded at the first, second and third quartile.}
\label{fig22}
\end{figure}
As observable statitics, we use 
%compute the horizontal and vertical perimeter of each thresholded image, thus obtaining for each level $t_{\alpha}$, $(P^{(1)}_{i}(t_{\alpha}))_{i \leq 245}$, count
the respective numbers of horizontal and vertical edges that separate a black pixel from a white pixel of the binary image. We name these counters as oriented perimeters, horizontal and vertical respectively. In case of an isotropic texture, the ratio of the two oriented perimeters should be close to one. At the opposite, if the observed ratio is far from one, then some anisotropy is expected in the microscopic texture of the image.

@@

The next step of our method consists in building the promised statistical test. More precisely, $\rho$ being the covariance function of the Gaussian field and $(e_1,e_2)$ being the canonical basis of $\mathbb R^2$, we consider the null hypothesis $H0:~\rho(e_1)=\rho(e_2)$ that we call "local isotropy" through a misuse of language. We exhibit a statistic depending on the ratio of the oriented perimeters that goes to one under $H0$ thanks to the CLT previously established. Moreover, we prove the consistency of the proposed test. Let us insist on the fact that our test is a non-parametric one so that the alternative hypothesis reduces to $H1:~\rho(e_1)\ne \rho(e_2)$.

@@

This result extends the one given in \cite{HermineAgnes} (Proposition 3) where the expected perimeter is computed in the case $\rho(e_i) > 0$. Using the former expression, we are also able to obtain an analytic expression for the first moment.

@@

Considering again the former expression, we get that 

@@

  \label{propEquationFisrtmoment2}

@@

with $N \sim \mathcal{N}\left(0,1\right)$, one should note that $\mathbb{E}\left(f^{(i)}(t)\right) = h_{t}\left(\rho(e_i)\right)$. We introduce an intermediate function $p_{t}(x) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$. Making use of the symmetry properties of the cumulative distribution function $\Phi$, \linebreak we have $h_{t}(x) =p_{t}(x) - 1 + p_{-t}(x)$, thus the derivative of $h_{t}$ is equal to $h_{t}'(x) = p_{t}'(x) + p_{-t}'(x)$ and 

@@

\end{align*}Thus, $h_{t}'(x) = 2 \times \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}} = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}}$ and besides $h(1) = 0$, which gives us the results.

@@

\item In the case of a fully dependent field, \textit{i.e}  $\rho(e_i) = 1$, $\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) \right) = 0$.
\item In the case of a highly dependent field, \textit{i.e} $\rho(e_i) \sim 1$ ,  from Equation \eqref{propEquationFisrtmoment2} note that we would be integrating over a small interval, therefore $\mathbb{E}\left(f^{(i)}(t) \right) \sim \frac{\sqrt{1-\rho(e_i)}}{\pi\sqrt{2}} \exp(-t^2/2)$, as it has been shown in \cite{HermineAgnes}. In that case, the ratio $\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)$ is invariant in regard to $t$. \textcolor{blue}{Demander a Hermine, comment on relie ce resultat a son papier}

@@

Let us consider a stationary Gaussian random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$ with zero mean and unit variance whose covariance structure is given by $\rho(x) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right)$ such that $|\rho(e_i)| < 1$ and that $\rho$ corresponds to a spectral measure that has a density.

@@

\textcolor{red}{mettre une remarque qui dit que l'existence de la densite spectral nous dit que si les les points sont distincts la covariance est inversible . Donc la somme se decompose en : j'ai 2 points, 3 ou 4 points, toruver une ref pour justifier tout ca} \\

Let us first start with the 2-cells case (\textit{see} Lemma \ref{2cells} below), which appears in the computation of the term $\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(0)\right)$, the 4-cells case, will be computed in the Proposition \ref{PropositionFourCell} and finally, the 3-cells case will be studied in the Appendix. Applying the same strategy we used to compute the first moment in Proposition \ref{propFisrtmoment}, we get the next result. \\

@@

\label{2cells}

@@

\label{CovarianceAffine}

@@

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{Variance_40_30_10_1.pdf}}
    \hspace{0.2cm}
 \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40, 30, 10,1$. }
\label{figVariance}
\end{figure}
\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{subwindowVarestimation.pdf}}
    \hspace{0.2cm}
 \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute, the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the subwindow estimation of the variance, the computations were done using an image of size $ m = 4800$, $C = 40$ and the size of $T_{i}$ equal $240\times240$, for the values $b = 1$ and $C = 40$. }
\label{figSubwindowVariance}
\end{figure}

@@

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiopvaluesubwindow.pdf}}
    \hspace{0.2cm} 
 \caption{We represent the $p_{\text{value}} = 2\mathbb{P}\left(Z \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $Z \sim \mathcal{N}(0,1)$ the estimation of the variance was done using an image of size $m = 4800$ and the size of $T_{i}$ being equal to $240\times240$  for different values of $b = 1, 1.2, 1.5, 2$ and $C = 40$.}
% \label{fig2}
\end{figure}
\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.4]{TestaniRatiopvaluetheta.pdf}}
    \hspace{0.2cm} 
 \caption{We represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/12, \pi/8, \pi/6, \pi/3$ and $C = 40$.}
% \label{fig2}
\end{figure}

\paragraph{Blind angle}It is important to note that we only test a form of local isotropy, with preferential axis $(e_1,e_2)$ there exist anisotropic models where $\rho(e_1) = \rho(e_2)$, like it is the case when $\theta = \pi/4$, in that case the model is clearly anisotropic as we can see Figure and the test will accept the hypothesis. \textcolor{red}{Add discussion about this, l'erreur de type 1 et 2.}
    {\includegraphics[scale=0.28]{Figurepi411.pdf}} \hspace{-1cm}
      {\includegraphics[scale=0.28]{Figurepi410.pdf}}
      \vspace{-3cm}
      \hspace{-0.5cm}
    {\includegraphics[scale=0.28 ]{TestaniRatiopvaluepi4}}
    % {\includegraphics[scale=0.25]{TestaniRatiopvaluepi410.pdf}}
    % \vspace{-3cm}
 \caption{On the first row we represent two generations of an affine Gaussian random fields with covariance of a compact support $\rho(x) = (1 - 3||Ax||_{2}/2C + (||Ax||_{2})^{3}/2C^{3})\mathbbm{1}_{||Ax||_{2} < C}$, as in \eqref{CovarianceAffine} with~$m = 512$, and $\theta = \pi/4$ and $C = 40$ respectively on the left $b = 1.1$ and $b = 10$, on the second row, we represent $p_{\text{value}} = 2\mathbb{P}\left(N \geq |z|\right)$ with $z = \frac{\mathbb{E}\left(R_{m,n}(t)\right) - 1)}{\sqrt{\hat{\mathbb{V}\left(R_{m, n}(t)\right)}}}$ and $N \sim \mathcal{N}(0,1)$ in blue color computed for a Montecarlo $= 2000$, for different values of $b = 1.1$ and $\theta = \pi/4$ and $C = 40$..}
    {\includegraphics[scale=0.4]{TestaniPhi0.pdf}}
 \caption{We represent the values of $\hat{\Phi}_{m}$ see Equation \eqref{phihat}, computed as a function of $b$ and a fixed value $t=0$ in blue color for a Montecarlo $= 2000$, and $C = 40$.}

@@

\subsection{Application of the local isotropy test to real world data}

@@

three French research hospitals (Amiens, Orleans and Cochin in Paris) \textcolor{red}{bien citer les refs des images}. Patients were recruited from a program originated by the hospital of Orleans between Nov. 2004 and Feb. 2006. We analyzed $n=245$ X-ray images of calcaneus bones. 
We first applied a pre-processing step in order to get stationary images. This step is performed by substracting the trend which is represented by a plane obtained via a mean-square linear regression. Furthermore, to avoid boundaries issues, we decided to crop from a $400\times400$  image to a $300\times300$ image, it is also necessary to standardize the images to be in the correct framework.

@@

 \caption{Example of images before (first row) and after (second row) the stationarization procedure and their respective excursion sets at quantile level $0.5$.}

@@

\paragraph{Applying the local isotropy test.}The first analysis of Figure \ref{figBoxplot} suggests the existence of two clusters in regard to the ratio of the two perimeters. Indeed, we observe a cluster of points for which the ratio $\mathcal{P}_{1}(q_{\alpha})/\mathcal{P}_{2}(q_{\alpha}) < 1$, which means that the corresponding images are mis-oriented. Thus, before proceeding further with the analysis, we apply a $\pi/2$-rotation to these images, which amounts to interchanging the values of $\mathcal{P}_{1}(q_{\alpha})$ and $ \mathcal{P}_{2}(q_{\alpha})$, here is the new boxplot that is obtained,

@@

 \caption{For $\alpha \in [0.15, 0.99]$, we represent the boxplot of the ratios $(R_{i}(q_{\alpha}))_{i \leq 245}$ between the two oriented perimeters computed at $t_{\alpha}$ level, for real thresholded images of bone X-rays and flipped images.}

@@

We can now proceed to the local isotropy test and comput the ratio $R_{i}(q_{\alpha}) = \mathcal{P}^{1,i}(t_{\alpha})/\mathcal{P}^{2,i}(t_{\alpha})$ for each image $i$ at quantile level $\alpha$, and then compute  \linebreak the $p_{value}(q_{\alpha}) = 2(1-\mathbb{P}\left(\mathcal{N} \leq \left|\overline{R}_{n}(q_{\alpha}) - 1)\right|/\overline{\sigma}_{n}(q_{\alpha})\right))$, $\overline{\sigma}_{n}(q_{\alpha})$ is estimated using the Montecarlo technique (\textcolor{red}{renvoyer a la partie sur l estimation et dire qui est Rm aussi, qu'on a fait une moyenne sur les Ri et mettre Ri en ordonnee}) . 

@@

 \caption{For $\alpha \in [0.15, 0.99]$, we represent the $p_{value}$ of the test computed for different levels $q_{\alpha}$ for real thresholded images of bone X-rays.}

@@

The values of $p_{value}$ are lower than $0.001$, except for extreme values of $q_{\alpha}$ (\textit{i.e} $\alpha = 0.99$), this leads us to reject $H_{0}$ which is the hypothesis of having local isotropy. Furthermore, when analyzing Figure \ref{Boxplotretournee}, the distribution of the ratio $\left(R_{i}(t)\right)_{i\leq n}$ seems to be invariant in regards to the threshold level as cited in Remark \ref{casdegenerer}, which suggests that the field is highly dependent. The next step consists in estimating $\rho(e_i)$ by using the total variation of the image and applying Proposition \ref{Variationtotal}. 

@@

Looking at Figure \ref{boxplotrho}, it confirms the highly dependence behavior of the field \textit{i.e} $\rho(e_1) \sim 1$ and $\rho(e_2) \sim 1$.
